Enter our title here

### 2017-08-22 manuscript.tex
Update manuscript.tex
testing merge
added SCTs and exercise overview

The goal for any introductory statistics course is to help students develope the ability to think statistically
\citep{AmericanStatisticalAssociation2016}.
Introducing technology into the curriculum can greatly strengthen this ability by illustrating statistical concepts such as
variability, randomness and simulation. Although numerous statistical technologies exist, \textit{R} and \textit{R Studio}
provide extensive statistical capabilites (free of charge) and are commonly used in statistics courses \citep{Chance2007}. R
allows students to explore real-world data sets which can not only enhance their understanding of concepts, but can also spark
an interest in the domain of statistics \citep{Wang2017}.

@@

*Swirl can be linked to a Coursera gradebook- learners can have swirl automatically notify coursera of a completed lesson
but this is not avaiblable for the classroom setting (coursera website) so should I include this?*

@@

A feature that set's DataCamp courses apart from competing technologies is the ability to track student progress. Educators
can set deadlines for assignments and easily see not only when students complete an assignment but also which sections the
students had trouble with in a detailed report (datacamp/teach website). Student scores can be automatically updated to a
current gradebook when you link the schools' learning management system (LMS) to DataCamp, allowing for a smooth integration.

@@

In the 'assignment' portion of the exercise, instructors can add additional information about the assignment that will help
students understand and complete the instructions. The Instructions section will contain the actual task the student is
asked to execute. The 'pre-exercise code' sets up the workspace for the student; this section will contain code to import
data sets, install packages and any other operation that you want to be in the workspace but hidden from students. The 'sample
code' section contains code or notes that students view in the R script panel. Students' also use the R script panel to write
the code that solves the tasks in the instructions. If students are not able to complete the task without help, they can click
on the 'Hint' button or eventually the 'solution'.

Solution Correctness Test code..

>>>>

The goal for any introductory statistics course is to help students develope the ability to think statistically
\citep{AmericanStatisticalAssociation2016}.
Introducing technology into the curriculum can greatly strengthen this ability by illustrating statistical concepts such as
variability, randomness and hypothesis testing. Although numerous statistical technologies exist, \textit{R} and \textit{R Studio}
provide extensive statistical capabilites (free of charge) and are commonly used in statistics courses \citep{Chance2007}. R
allows students to explore real-world data sets which can not only enhance their understanding of concepts, but can also spark
an interest in the domain of statistics \citep{Wang2017}.

@@

While swirl can be linked to a Massive Open Online Courses (MOOCs) like Coursera through API, this is not avaiblable for the classroom
learning management systems (LMS).

@@

A feature that sets DataCamp apart from competing technologies is the ability to track student progress. Educators
can set deadlines for assignments and easily see not only when students complete an assignment but also which sections the
students had trouble with in a detailed report (datacamp/teach website). Student scores can be automatically updated to a
current gradebook when you link the schools' learning management system (LMS) to DataCamp, allowing for a smooth integration of student work.

@@

The submission correctness testing code (or SCT) is the backbone for DataCamp's interactive nature. If a student submits an incorrect answer, they will 
receive immediate feedback on what they are doing wrong and the system will guide them to the right answer. Instructors can use the default feedback
that DataCamp automatically generates or write their own custom messages. The default feedback is meaningful and specific; most of the time custom messages
are not necessary unless there is a common problem that student are struggling with in which more unique feedback is necessary. DataCamp provides a helpful
R package called 'testwhat' which acts as a guide to writing the SCTs. 'testwhat' contains functions that can test different types of problems including
loops, object definitions, printed output, functions, ect (datacamp website), this submission correctness testing code compares the ideal answer (from the 
solution) to the students answer. Different arguements can be added to the test functions to alter the testing process and automatic feedback.

**add an example of a test_function sct

In the 'assignment' portion of the exercise, instructors can add additional information about the assignment that will help
students understand and complete the instructions. The Instructions section will contain the actual task the student is
asked to execute. The 'pre-exercise code' sets up the workspace for the student; this section will contain code to import
data sets, install packages and any other operation that you want to be in the workspace but hidden from students. The 'sample
code' section contains code or notes that students view in the R script panel. Students also use the R script panel to write
the code that solves the tasks in the instructions. If students are not able to complete the task without help, they can click
on the 'Hint' button or eventually the 'solution'. When the student clicks the 'Submit Code' button, their answer passes through the SCT code where the
code is checked for errors.

**add example of a normal coding exercise

The 'MultipleChoiceExercise', as you would expect, contains a question and a list of various answers. Instructors write the questions in the 'lesson' 
portion of the exercise and offer solutions in the 'Insruction' section. Like the 'normal' coding exercises, the lesson, instructions, pre-exercise code and
SCTs have to be specified but sample and solution code do not. There are two types of multiple choice questions, simple and regular. The simple multiple 
choice exercises are used for questions that do not require the R console or any R output. Regular multiple choice exercises allow instructors to pre
-program objects or plots that the student needs to access to answer the question. Both types of multiple choice exercises are straightforward to write can 
act as quick checks for understanding throughout the chapter.

**add example of regular multiple choice exercise

Video exercises act as in instructional video addition to a DataCamp course; instructors can add short videos of them explaining concepts and with relevent slides that appear in the background. The DataCamp website \url{https://www.datacamp.com/teach/documentation#tab_code_exercises} provides more detail on the content of the various exercises.
